---
title: "Statistical inference part 2"
author: "Sergei Keidzh"
date: 'May 13 2018'
output: html_document
---
```{r}
setwd("C:/Users/Клеопатра/Desktop/serg/data/statistical inference")
library(datasets)
library(ggplot2)
data(ToothGrowth)
str(ToothGrowth)
head(ToothGrowth)
```
#to make it reproducible it's better to convert variable to factor 
#in this case variable dose 
```{r}
ToothGrowth$dose <- as.factor(ToothGrowth$dose)
```
#let's review again 
```{r}
str(ToothGrowth)
```
#provide a basic summary
```{r}
summary(ToothGrowth)
```
# split of cases between different dose levels and delivery methods
```{r}
table(ToothGrowth$dose, ToothGrowth$supp)
ggplot(data=ToothGrowth, aes(x=as.factor(dose), y=len, fill=supp))+
  geom_bar(stat="identity",)+
  facet_grid(. ~ supp)+
  xlab("Dose")+
  ylab("Tooth length")+
  guides(fill=guide_legend(title="Supplement type"))
```
#on the figure we can see how vitamin C influenced in positive way on
#tooth length which has been dependend on dose of vitamin. 

#Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose. 
#(Only use the techniques from class, even if there's other approaches worth considering)
```{r}
data2 <- lm(len ~ dose + supp, data=ToothGrowth)

summary(data2)
```
#As we can see the Vitamin C provides more tooth growth than ascorbic acid at lower dosages (0.5 Mg - 1 Mg).
#The tooth growth rate is not statistically different between supplement methods at the higher dosage
#Dose is  the key factor in tooth growth. If the dose is  more higher, the more grow for the teeth.
#The variances between the sample popluations are not equal
#The sample data is not paired
#The sample population distribution is mound shaped and not skewed